
\documentclass[a4paper,12pt]{article}

\usepackage{fontspec}
\usepackage{dblfnote}
\usepackage{pfnote}

\setromanfont{Skolar PE}

\linespread{1.5}
\spaceskip 0.5em

\begin{document}

% ('VERSE_RANGE_START', ('041801', '041811'))
% ('BOOK_START', 4)
\textbf{\Large 18.1}
Ταῦτα
εἰπὼν
Ἰησοῦς
ἐξῆλθεν
σὺν
τοῖς
μαθηταῖς
αὐτοῦ
πέραν\footnote{πέραν \textendash\ \textit{on the other side}}
τοῦ
χειμάρρου\footnote{χείμαρρος, ου, ὁ \textendash\ \textit{ravine}}
τοῦ
Κεδρὼν\footnote{Κεδρών, ὁ \textendash\ \textit{Kidron}}
ὅπου
ἦν
κῆπος,\footnote{κῆπος, ου, ὁ \textendash\ \textit{garden}}
εἰς
ὃν
εἰσῆλθεν
αὐτὸς
καὶ
οἱ
μαθηταὶ
αὐτοῦ.
% ('VERSE_END', 1)
\textbf{2}
ᾔδει
δὲ
καὶ
Ἰούδας
ὁ
παραδιδοὺς
αὐτὸν
τὸν
τόπον,
ὅτι
πολλάκις\footnote{πολλάκις \textendash\ \textit{many times, often}}
συνήχθη
Ἰησοῦς
ἐκεῖ
μετὰ
τῶν
μαθητῶν
αὐτοῦ.
% ('VERSE_END', 2)
\textbf{3}
ὁ
οὖν
Ἰούδας
λαβὼν
τὴν
σπεῖραν\footnote{σπεῖρα, ης, ἡ \textendash\ \textit{cohort}}
καὶ
ἐκ
τῶν
ἀρχιερέων
καὶ
ἐκ
τῶν
Φαρισαίων
ὑπηρέτας\footnote{ὑπηρέτης, ου, ὁ \textendash\ \textit{officer}}
ἔρχεται
ἐκεῖ
μετὰ
φανῶν\footnote{φανός, οῦ, ὁ \textendash\ \textit{lamp}}
καὶ
λαμπάδων\footnote{λαμπάς, άδος, ἡ \textendash\ \textit{torch}}
καὶ
ὅπλων.\footnote{ὅπλον, ου, τό \textendash\ \textit{weapon}}
% ('VERSE_END', 3)
\textbf{4}
Ἰησοῦς
οὖν
εἰδὼς
πάντα
τὰ
ἐρχόμενα
ἐπ’
αὐτὸν
ἐξῆλθεν,
καὶ
λέγει
αὐτοῖς·
Τίνα
ζητεῖτε;
% ('VERSE_END', 4)
\textbf{5}
ἀπεκρίθησαν
αὐτῷ·
Ἰησοῦν
τὸν
Ναζωραῖον.\footnote{Ναζωραῖος, ου, ὁ \textendash\ \textit{Nazarene}}
λέγει
αὐτοῖς·
Ἐγώ
εἰμι.
εἱστήκει
δὲ
καὶ
Ἰούδας
ὁ
παραδιδοὺς
αὐτὸν
μετ’
αὐτῶν.
% ('VERSE_END', 5)
\textbf{6}
ὡς
οὖν
εἶπεν
αὐτοῖς·
Ἐγώ
εἰμι,
ἀπῆλθον
εἰς
τὰ
ὀπίσω
καὶ
ἔπεσαν
χαμαί.\footnote{χαμαί \textendash\ \textit{on the ground}}
% ('VERSE_END', 6)
\textbf{7}
πάλιν
οὖν
ἐπηρώτησεν
αὐτούς·
Τίνα
ζητεῖτε;
οἱ
δὲ
εἶπαν·
Ἰησοῦν
τὸν
Ναζωραῖον.\footnote{Ναζωραῖος, ου, ὁ \textendash\ \textit{Nazarene}}
% ('VERSE_END', 7)
\textbf{8}
ἀπεκρίθη
Ἰησοῦς·
Εἶπον
ὑμῖν
ὅτι
ἐγώ
εἰμι·
εἰ
οὖν
ἐμὲ
ζητεῖτε,
ἄφετε
τούτους
ὑπάγειν·
% ('VERSE_END', 8)
\textbf{9}
ἵνα
πληρωθῇ
ὁ
λόγος
ὃν
εἶπεν
ὅτι
Οὓς
δέδωκάς
μοι
οὐκ
ἀπώλεσα
ἐξ
αὐτῶν
οὐδένα.
% ('VERSE_END', 9)
\textbf{10}
Σίμων
οὖν
Πέτρος
ἔχων
μάχαιραν\footnote{μάχαιρα, ης, ἡ \textendash\ \textit{dagger}}
εἵλκυσεν\footnote{ἕλκω \textendash\ AAI 3S \textendash\ \textit{draw}}
αὐτὴν
καὶ
ἔπαισεν\footnote{παίω \textendash\ AAI 3S \textendash\ \textit{strike}}
τὸν
τοῦ
ἀρχιερέως
δοῦλον
καὶ
ἀπέκοψεν\footnote{ἀποκόπτω \textendash\ AAI 3S \textendash\ \textit{cut off}}
αὐτοῦ
τὸ
ὠτάριον\footnote{ὠτάριον, ου, τό \textendash\ \textit{ear}}
τὸ
δεξιόν.
ἦν
δὲ
ὄνομα
τῷ
δούλῳ
Μάλχος.\footnote{Μάλχος, ου, ὁ \textendash\ \textit{Malchus}}
% ('VERSE_END', 10)
\textbf{11}
εἶπεν
οὖν
ὁ
Ἰησοῦς
τῷ
Πέτρῳ·
Βάλε
τὴν
μάχαιραν\footnote{μάχαιρα, ης, ἡ \textendash\ \textit{dagger}}
εἰς
τὴν
θήκην·\footnote{θήκη, ης, ἡ \textendash\ \textit{sheath}}
τὸ
ποτήριον
ὃ
δέδωκέν
μοι
ὁ
πατὴρ
οὐ
μὴ
πίω
αὐτό;
% ('VERSE_END', 11)
% ('CHAPTER_END_PARTIAL', 18)
% ('BOOK_END_PARTIAL', 4)
% ('VERSE_RANGE_END', ('041801', '041811'))
\end{document}
